The yaq Project: \\ A Standard for Scientific Instrumentation

### 2022-10-26 paper.tex
fixed sentences at beginning of section to yield proper barrier designations

In this section we describe the architecture of the \yaq{} framework in light of three major barriers that we have encountered in scientific instrumentation development.
First barrier: Multiple interfaces are used to communicate with each component of the system.
A fully automated system must be able to use all of these interfaces, a daunting task for scientists who do not specialize in software development.
Second barrier: Certain specialty hardware have inconvenient interface requirements.
A camera will only work with an obsolete interface card and drivers for Windows XP.
A data acquisition manufacturer provides an Application Programmer Interface (API) that only works in Python 3.7.
A graduate student wishes to drive several stepper motors using a Raspberry Pi.
Third barrier: Some hardware interfaces are blocking.
A graphical user interface stalls while waiting for a camera to collect data.
Custom orchestration software needs to be closed before the manufacturers configuration software can be used.
A graduate student finds themself needing to master advanced concepts in concurrency in order to orchestrate many motors performantly.

@@

The second hardware interface barrier: Reduction of the interfacing code to an easier-to-manage subset of that available.  Here, we implement an approach useful for
systems integration in the sciences which we call a Minimal Programming Interface (MPI).   The MPI is essentially a reduced set of functions found in the hardware API.   The MPI 
 is defined as the minimal set of API functions for a given hardware component concluded by the researchers as necessary for the fuller system development. 
 The value of this MPI is that it can be formed by wrapping and/or converting the API from its native language into a language known to be transparent to researchers, such as the programming
 language Python.  The \yaq{} traits feature acts as a tool in exposing the MPI from the base APIs often supplied by the hardware manufacturer, as the traits
 automatically define the primary set of key functions, and any additionally required functions are added by the researcher on top of the primary set.

>>>>

In this section we describe the architecture of the \yaq{} framework in light of three major barriers that we have encountered in scientific instrumentation development.
First barrier: Multiple interfaces are used to communicate with each component of the system.
A fully automated system must be able to use all of these interfaces, a daunting task for scientists who do not specialize in software development.
Second barrier: Coding interfaces adds to a maintenance overhead seldom manageable by researchers.   Updates to the hardware and operating systems often
require maintenance updates to interfacing code that is not maintainable as researchers are not usually delegated to be strictly software maintainers.
Third barrier: Certain specialty hardware have inconvenient interface requirements.
A camera will only work with an obsolete interface card and drivers for Windows XP.
A data acquisition manufacturer provides an Application Programmer Interface (API) that only works in Python 3.7.
A graduate student wishes to drive several stepper motors using a Raspberry Pi.
Fourth barrier: Some hardware interfaces are blocking.
A graphical user interface stalls while waiting for a camera to collect data.
Custom orchestration software needs to be closed before the manufacturers configuration software can be used.
A graduate student finds themself needing to master advanced concepts in concurrency in order to orchestrate many motors performantly.

@@

The second hardware interface barrier:  Coding interfaces adds to a maintenance overhead seldom manageable by researchers.  Here, we implement an approach useful for
systems integration in the sciences which we call a Minimal Programming Interface (MPI).   The MPI is essentially a reduced set of functions found in the hardware API.   The MPI 
 is defined as the minimal set of API functions for a given hardware component concluded by the researchers as necessary for the fuller system development. 
 The value of this MPI is that it can be formed by wrapping and/or converting the API from its native language into a language known to be transparent to researchers, such as the programming
 language Python.  The \yaq{} traits feature acts as a tool in exposing the MPI from the base APIs often supplied by the hardware manufacturer, as the traits
 automatically define the primary set of key functions, and any additionally required functions are added by the researcher on top of the primary set.
